\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-07-03 paper/subdocuments/data.Rnw
fixed issue with invisible tables (remove table env)

\begin{table}[h]
\begin{tabular}{lcccc}
                                   & FTA       & Survey data\\
Statistical unit                   & Tax units (individuals/married couples)  & Households\\                                   
Concepts of economic resources  & Data-driven   & Theory-driven\\
Population coverage & total population & sample \\ 
Top incomes covered                 & Yes   & No\\
Low incomes covered?               & no        & yes\\
Comparison over time possible 	   & Long       & Short \\
Cross country comparison possible? & limited   & possible

\end{tabular}
\end{table}

%RF: damit haben wir WER, WANN, WAS, wollen wir noch ein WOMIT/WAS DARSTELLEN -> methodik -> reldist ? jaa

>>>>

\multicolinterrupt{
\begin{table}[H]
\caption{\label{datacomp}} 
\begin{center}
\begin{tabular}{lcc}
\hline\hline
                                   & FTA       & Survey data\\
\hline
Statistical unit                   & Tax units (individuals/married couples)  & Households\\                                   
Concepts of economic resources  & Data-driven   & Theory-driven\\
Population coverage & total population & sample \\ 
Top incomes covered                 & Yes   & No\\
Low incomes covered?               & no        & yes\\
Comparison over time possible 	   & Long       & Short \\
Cross country comparison possible? & limited   & possible\\
\hline
\end{tabular}
\end{center}
\end{table}
}
%RF: damit haben wir WER, WANN, WAS, wollen wir noch ein WOMIT/WAS DARSTELLEN -> methodik -> reldist ? jaa
